### 2020-10-15 thesis/msc-thesis.tex
new table of content

% MAIN PART:
% Table of contents (Inhaltsverzeichnis)
\tableofcontents
\cleardoublepage
\pagenumbering{arabic}

% List of figures (Abbildungsverzeichnis):
%\listoffigures
% List of tables (Tabellenverzeichnis):
%\listoftables

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Introduction}\label{intro}

\section{Motivation}

\subsection{Evolution of digital Customer Self-Service}
\begin{enumerate}
     \item Increasing consumer standards
           \begin{enumerate}
                \item Passwordless sign in
                \item instant updates
           \end{enumerate}

     \item New regulations
           \begin{enumerate}
                \item DSGVO
                \item Onlinezugangsgesetz
                \item DVG (eAU, eRezept)
                \item psd2
           \end{enumerate}

\end{enumerate}

\subsection{CSS as a Service}
\begin{enumerate}
     \item Enterprises can offer CSS service, satisfying modern requirements and regulations
\end{enumerate}

\subsection{Service Integration}
\begin{enumerate}
     \item The provided CSS service has to be integrated into existing enterprise architecture
\end{enumerate}

\section{Goals of the work}

Solution for integration challenges
\begin{enumerate}
     \item Heterogeneous Enterprise Architecture Systems
           \begin{enumerate}
                \item Different Applications
                \item Different Application Vendors
                \item Different / No Application Interfaces
                \item Legacy Systems
           \end{enumerate}

     \item Different (proprietary) data models within and between Enterprises and Organizations
           \begin{enumerate}
                \item Different (property)name for same data objects (syntactic integration)
                \item Different meanings for same (property)name (semantic integration)
           \end{enumerate}

     \item Stability of Integration
           \begin{enumerate}
                \item Future Changes of EA
                \item Scalability
                \item Failure of EA or Integration Components
           \end{enumerate}

     \item Scarce Resources
           \begin{enumerate}
                \item Integration Development Speed
                      \begin{enumerate}
                           \item Necessary Development <=> Reuse of existing Technology
                           \item Complexity / Size of Integration
                      \end{enumerate}

                \item Maintenance of finished Integration

                \item Hardware / Software Costs of Integration
                      \begin{enumerate}
                           \item Licenses for Software
                           \item Scalability of Integration => Necessary Computing Power
                      \end{enumerate}

           \end{enumerate}

\end{enumerate}

\section{Structure of the work}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

\chapter{Foundation and related work}

\section{Customer Self-Service}
\begin{enumerate}
     \item Definition in the context of the thesis
     \item Purpose in Thesis
     \item Overview of CSS-Scenarios found in literature
\end{enumerate}

\section{Architecture Patterns}
\begin{enumerate}
     \item Definition
     \item Purpose in Thesis
     \item Explanation of used Patterns
\end{enumerate}

\subsection{Business Connector}
\begin{enumerate}
     \item Definition in context of the thesis
     \item Purpose in Thesis
\end{enumerate}

\section{Messaging Patterns}
\begin{enumerate}
     \item Definition
     \item Messaging
           \begin{enumerate}
                \item Answer: Why is messaging used?
           \end{enumerate}
     \item Patterns
           \begin{enumerate}
                \item Answer: Why are patterns used?
           \end{enumerate}
     \item Explanation of used patterns
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

\chapter{Groundwork}

\subsection{CSS-Scenarios}
\begin{enumerate}
     \item Categorization of Scenarios
     \item Combining similar scenarios (into a more general one)
     \item Prioritization
     \item ToDo: How to document?
     \item Documentation of final list
\end{enumerate}

\subsection{Enterprise Architecture}
\begin{enumerate}
     \item Architecture- and Data bricks
           \begin{enumerate}
                \item Selection of EAPs relevant for CSS
                      \begin{enumerate}
                           \item Derived by comparing CSS-Scenarios with business processes
                      \end{enumerate}
                \item Evaluation of Architecture bricks and data bricks of EAPs relevant for CSS-Scenarios
                \item Documentation of resulting Architecture and data bricks
           \end{enumerate}

     \item Requirements of Enterprise Architecture
           \begin{enumerate}
                \item List of requirements towards the integration Architecture
                      \begin{enumerate}
                           \item Adapters for systems
                           \item Required Format of incoming data
                      \end{enumerate}
           \end{enumerate}
\end{enumerate}

\section{Business Connector}
\begin{enumerate}
     \item How to document the business Connector
     \item List of provided functionalities along with their interfaces
           \begin{enumerate}
                \item Derived from CSS-Scenarios
                \item Derived from IDAS Connector
           \end{enumerate}

     \item List of requirements regarding the EA
           \begin{enumerate}
                \item Access to architecture and data bricks
           \end{enumerate}

     \item List of requirements regarding the integration Architecture
           \begin{enumerate}
                \item Format of data
                \item Order of delivery
                \item Time relevance of data
                \item Guaranteed delivery of data
           \end{enumerate}

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

@@

\section{Overview}

\begin{enumerate}
     \item Requirements of Enterprise Architecture
     \item Requirements of Business Connector
     \item Requirements of Integration System
\end{enumerate}

\subsection{Requirements of Enterprise Architecture}

\subsection{Requirements of Business Connector}

\subsection{Requirements of Integration System}

\section{Scenario Integrations}
\begin{enumerate}
     \item Look at integration architecture for each CSS-Scenario
\end{enumerate}

\subsection{Integration Architecture Documentation Method}
\begin{enumerate}
     \item Entity Diagram(s)
     \item Flow Diagram(s)
     \item etc.
\end{enumerate}

\subsection{Scenario1}
\begin{enumerate}
     \item Description of Scenario
\end{enumerate}

\subsubsection{Scenario1 Integration Architecture}
\begin{enumerate}
     \item Entity Diagram(s)
     \item Flow Diagram(s)
     \item etc.
\end{enumerate}

\subsubsection{System Integration}
\begin{enumerate}
     \item Explanation how the systems are integrated
     \item Why was each pattern used?
     \item How are requirements met?
\end{enumerate}

\subsubsection{Data Integration}
\begin{enumerate}
     \item Explanation how the data objects are integrated
     \item Why was data transformed / mapped?
     \item How are requirements met
\end{enumerate}

\subsection{Scenario2}

\subsubsection{Scenario2 Integration Architecture}

\subsubsection{System Integration}

\subsubsection{Data Integration}

\chapter{Evaluation}

\section{Technological Evaluation}

\subsection{Available Messaging Technologies}

\subsection{Implementation of Integration Architecture}

\subsection{Evaluation of result}

\section{Experimental Evaluation}

\subsection{Customer Example}

\subsection{Application of Integration Architecture}

\subsection{Evaluation of result}

\section{Operation Manual}
\begin{enumerate}
     \item Guide on how to implement and deploy the integration architecture
     \item incorporates results of previous evaluations
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Summary and outlook}

% References (Literaturverzeichnis):
% a) Style (with abbreviations: use alpha):
% see
% https://de.wikibooks.org/wiki/LaTeX-W%C3%B6rterbuch:_bibliographystyle
% for the different formats and styles

\bibliographystyle{apalike}
% b) The File:
\bibliography{references}

>>>>

\tableofcontents
\cleardoublepage
\pagenumbering{arabic}

\chapter{Context}

The german ministry of economy and energy recognizes that "we have long since arrived in a digitized world". This realization 
of the german government comes along with important federal and european legislation. Most prominent are DSGVO, OZG and DVG, 
modernizing data protection, governmental administration and health care.

Enterprises, organizations and authorities are required to provide additional digital services for its customers and users.
Those include for example the deletion of non-mandatory data and the digital application for unemployment benefit.

Working with existing system- and data architectures, integration of new solutions is necessary.

\chapter{Objectives}

This bachelor thesis describes digital self-service as a solution for the additional requirements. It explains the basis of what 
customer self-service (CSS) is, what relevant legislation is about and how CSS providers can help in the digital transformation.

The technological challenge of integrating CSS providers into existing system architectures is focus of this bachelor thesis.
An integration architecture is presented, which provides solutions for the following questions (ToDo: In Textform schreiben):

\begin{enumerate}
     \item How can services of a CSS provider be accessed by the enterprise architecture?
     \item Which systems of a typical enterprise architecture are required?
     \item Which data objects of a typical enterprise architecture are required?
     \item Which additional systems and data objects are required?
     \item How can heterogeneous enterprise architectures be integrated the same way?
     \item How can the integration be non-invasive?
     \item How can the speed of integration development be increased?
     \item How can the speed of integration deployment be increased?
     \item How can the integration system be reliable and maintainable?
\end{enumerate}

The architecture is evaluated in respect to technological feasibility and real-life applicability. The results are incorporated into 
an operating manual, providing guidance in developing and deploying the presented integration architecture.

\chapter{Structure of Work}

\chapter{Customer Self-Service (CSS)}

\section{Definition}

\section{Description}

\section{Benefits}

\subsection{Customer}

\subsection{Organization}

\section{Examples}

\chapter{Governmental Regulations}

\section{Purpose}

\section{Importance for Organizations}

\section{DSGVO}

\section{OZG}

\section{DVG}

\section{Challenges for Organizations}

\chapter{Compliance through CSS}

\section{Description}

\section{CSS-Scenarios}

\chapter{CSS Providers}

\section{Description}

\section{CSS Solutions}

\section{Business Connector}

\chapter{Enterprise Architectures}

\section{Modeling of the real world}

\section{Modeling Challenges}

\section{Enterprise Architecture Patterns (EAP)}

\chapter{Relevant Systems and Data}

\section{EAPs}

\section{Architecture Bricks}

\section{Data Bricks}

\section{Integration Requirements}

\subsection{Regarding Integration Architecture}

\subsection{Regarding Business Connector}

\chapter{Integration}

\section{Definition}

\subsection{Loose Coupling}

\subsection{Homogeneous Landscapes}

\section{Enterprise Integration Patterns (EIP)}

\subsection{Pattern 1}

\subsection{Pattern 2}

\chapter{Business Connector}

\section{Functionalities and Interfaces}

\section{Integration Requirements}

\subsection{Regarding Enterprise Architecture}

\subsection{Regarding Integration Architecture}

\section{Documentation}

\subsection{Connector as Architecture Brick}

@@

\section{Scenario 1}

\subsection{Integration Documentation}

\subsection{System Integration}

\subsection{Data Integration}

\section{Scenario 2}

\subsection{Integration Documentation}

\subsection{System Integration}

\subsection{Data Integration}

\chapter{Integration Architecture Evaluation}

\section{Technology}

\section{Customer Example}

\section{Operating Manual}

\bibliographystyle{apalike}
\bibliography{references}
